### 2015-05-15 corral.tex
fix

\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} after each shared memory access of each entry point, and after every lock and unlock operation.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: if, thanks to \whoop's analysis, we know that a given statement that accesses shared memory cannot be involved in a data race, we do not instrument a \texttt{yield} after this statement.  This is a form of \emph{partial order reduction}~\cite{DBLP:books/sp/Godefroid96}, and reduces the number of context switches that \corral must consider in a \emph{sound} manner: there is no impact on the bugs that will be detected.  This is because each access, for which a \texttt{yield} is suppressed, is guaranteed to be protected by some lock (a consequence of lockset analysis).  If the access is a write, its effects are not visible by the other entry point in the pair until the lock is released.  If the access is a read, the value of the shared location cannot change until the lock is released.  The fact that a \texttt{yield} is placed after each unlock operation suffices to take account of communication between entry points via the shared memory location.

>>>>

\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} after each shared memory access of each entry point, and after every lock and unlock operation.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: if, thanks to \whoop's analysis, we know that a given statement that accesses shared memory cannot be involved in a data race, we do not instrument a \texttt{yield} after this statement.  This is a form of \emph{partial order reduction}~\cite{DBLP:books/sp/Godefroid96}, and reduces the number of context-switches that \corral must consider in a \emph{sound} manner: there is no impact on the bugs that will be detected.  This is because each access, for which a \texttt{yield} is suppressed, is guaranteed to be protected by some lock (a consequence of lockset analysis).  If the access is a write, its effects are not visible by the other entry point in the pair until the lock is released.  If the access is a read, the value of the shared location cannot change until the lock is released.  The fact that a \texttt{yield} is placed after each unlock operation suffices to take account of communication between entry points via the shared memory location.

### 2015-05-15 whoop.tex
fix

First, we enriched \whoop with information regarding \emph{kernel-imposed serialization}, to increase precision. The Linux kernel can serialize calls to entry points, thus forcing them to run sequentially with each other. As an example, a large number of networking entry points are mutually serialized with RTNL, a network-specific kernel lock. We discovered this when we first analyzed the r8169 driver (see \S\ref{evaluation}) and \whoop reported many races between a number of networking entry points; when we investigated the source of these races, we found out that these entry points could not race in reality because of RTNL. \whoop exploits this knowledge and does not create pairs for entry points that are serialized by the kernel. This is an ongoing manual effort: the more drivers we study, the more such properties we discover, which we can then exploit to make \whoop more precise. Currently, this information is hard-coded inside \whoop. In the future, we plan to provide a configuration file where the user can denote such kernel specific information.

>>>>

First, we enriched \whoop with information regarding \emph{kernel-imposed serialization}, to increase precision. The Linux kernel can serialize calls to entry points, thus forcing them to run sequentially with each other. For example, a large number of networking entry points are mutually serialized with RTNL, a network-specific kernel lock. We discovered this when \whoop reported many races between a number of networking entry points of the r8169 driver (see \S\ref{evaluation}); when we investigated the source of these races, we found out that these entry points could not race in reality because of RTNL. \whoop exploits this knowledge and does not create pairs for entry points that are mutually serialized by the kernel. This is an ongoing manual effort: the more drivers we study, the more such properties we discover to make \whoop more precise. Currently, this information is hard-coded inside \whoop. In the future, we plan to provide a configuration file where the user can denote such kernel-specific information.
